Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-03 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

# II. Literature Review  
There is tons of published literature on the effects of home-court advantage.
Many of which mainly focus on the effects of home-court advantage using shooting
in the NBA. @Kotecki studies the impact of home-court advantage on winning in the
NBA. Kotecki proves the existence of home-court advantage using performance-based
statistics, specifically field goal percentage, free throw percentage, and 
points. All of which he proves significantly improved from home-court advantage, 
indicating home-court helps teams play better. This conclusion comes from 
comparing home performance vs. away performance in games. @Cao studied the effects
of pressure on performance in the NBA. They use free throws as their measure of 
interest, and research home and away factors in the study. They expected that home
fans could distract and put pressure on opposing players to make free throws,
which would negatively impact away team shooting. Likewise, the home team
would see a positive effect on free throw shooting. However, they find insignificant
evidence that home status has a substantial impact on missing from the free throw 
line. @Harris use two point shots, three-point shots and free throws as measures
of interest to study home-court advantage. They find that two point shots are
the strongest predictor of home-court advantage. They suggest that evidence 
supports that home teams should try to shoot more two point shots and force
their opponent to take more two point shot attempts. This strategy will maximize
the benefits of home-court advantage and give them the best chance to win.

>>>>

# II. Literature Review  
There is tons of published literature on the effects of home-court advantage.
Many NBA home-court advantage studies analyze the effects by studying shooting
percentages. @Kotecki examines the impact of home-court advantage on winning in the
NBA. Kotecki proves the existence of home-court advantage using performance-based
statistics, specifically field goal percentage, free throw percentage, and 
points. All of which he proves significantly improved from home-court advantage, 
indicating home-court helps teams play better. This conclusion comes from 
comparing home performance vs. away performance in games. @Cao studied the effects
of pressure on performance in the NBA. They use free throws as their measure of 
interest, and research home and away factors in the study. They expected that home
fans could distract and put pressure on opposing players to make free throws,
which would negatively impact away team shooting. Likewise, the home team
would see a positive effect on free throw shooting. However, they find insignificant
evidence that home status has a substantial impact on missing from the free throw 
line. @Harris use two point shots, three-point shots and free throws as measures
of interest to study home-court advantage. They find that two point shots are
the strongest predictor of home-court advantage. They suggest that evidence 
supports that home teams should try to shoot more two point shots and force
their opponent to take more two point shot attempts. This strategy will maximize
the benefits of home-court advantage and give them the best chance to win.
